Recurrent Neural Networks for object detection

### 2019-06-29 Paper/Paper_First_Draft.tex
adding preliminary details for three feature level papers

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Bin Qassim Ahmad}
\IEEEauthorblockA{\textit{Technical University of Munich} \\
\textit{Department of Informatics}\\
Munich, Germany \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Pettirsch Arnd}
\IEEEauthorblockA{\textit{Technical University of Munich)} \\
\textit{Department of Informatics}\\
Munich, Germany \\
a.pettirsch@outlook.de}
}

@@

\subsection{Image and Video Object Detection in general}
ToDo

@@

\subsection{Feature Selective Small Object Detection via Knowledge-based recurrent attentive neural networks}
ToDo

\subsection{Looking fast and slow: memory-guided mobile video object detection}
Todo

\subsection{Delving Deeper into Convolutional Networks for Learning Video Represenations}
ToDo

\subsection{Detect to Track and track to detect}
ToDo

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Bin Qasim Ahmad}
\IEEEauthorblockA{\textit{Technical University of Munich} \\
\textit{Department of Informatics}\\
Munich, Germany \\
ahmad.qasim@tum.de }
\and
\IEEEauthorblockN{2\textsuperscript{nd} Pettirsch Arnd}
\IEEEauthorblockA{\textit{Technical University of Munich)} \\
\textit{Department of Informatics}\\
Munich, Germany \\
a.pettirsch@outlook.de}
}

@@

\subsection{Image and Video Object Detection in general}
\begin{itemize}
	\item Image object detection history.
	\begin{itemize}
		\item Bayesian methods before deep learning
		\item ImageNet challenge and VID [15]
		\item Deep Learning and AlexNet [16]
	\end{itemize}
	\item Single stage and 2-stage image object detectors.
	\begin{itemize}
		\item A two-stage pipeline firstly generates region proposals, which are then classified and refined. [17]
		\item A single-stage method is often more efficient but less accurate. Directly regress on bounding boxes and classes. [18], [19]
	\end{itemize}
	\item Why is video object detection harder?
	\begin{itemize}
		\item Large size
		\item Motion blur
		\item Quality of the dataset
		\item Partial occlusion
		\item Unconventional Poses
	\end{itemize}
\end{itemize}

@@

\subsection{Feature Selective Small Object Detection via Knowledge-based recurrent attentive neural networks}
\includegraphics[width=\columnwidth]{KB-RANN-architecture}
\begin{itemize}
	\item Compute feature maps using a modified SqueezeNet architecture.
	\item Propagate the features through a Recurrent Attentive Neural Network, comprised of:
	\begin{itemize}
		\item Attention Mechanism to detect key areas within the feature maps.
		\item Convolutional LSTM for temporal feature propagation.	
	\end{itemize}
	\item Reverse gaussian feature maps are combined with the maps obtained from Conv. LSTM.
	\begin{itemize}
		\item These feature maps are based on learnable mean and covariance terms.
		\item This prior knowledge is derived from the assumption that traffic signs are always located at the bias of the center.

	\end{itemize}
\end{itemize}

\subsection{Looking fast and slow: memory-guided mobile video object detection}
\includegraphics[width=\columnwidth]{looking-fast-and-slow-architecture}
\begin{itemize}
	\item Run multiple feature extractors sequentially or concurrently to obtain feature maps.
	\begin{itemize}
		\item 	The idea is to use small and large feature extractors to optimize performance.
	\end{itemize}
	\item Aggregate and refine these feature maps using convolutional LSTM based memory network.
	\begin{itemize}
		\item To improve speed of LSTM network, add skip connections and LSTM state groups.
	\end{itemize}
	\item Apply SSD-style detection on refined features to obtain classification and bounding boxes.
	\item Use a reinforcement learning based policy for selection of which feature extractor to run.
	\item Large and small frame extractors can run in parallel using asynchronous mode.
\end{itemize}

\subsection{Detect to Track and track to detect}
\includegraphics[width=\columnwidth]{D&T-architecture}
\begin{itemize}
	\item Compute Convolutional feature maps using a Resnet-101 architecture.
	\item Use a RPN (region proposal network) to find candidate regions in the frame.
	\item ROI Pooling layer, to classify boxes and refine their coordinates (regression).
	\item Find correlation features between two frames’ feature maps and do ROI tracking.
	\item Due to memory constraints, use tracklets, which are class-based optimal paths in video.

\end{itemize}
